TKT RNAseq Experiment: Differential Expression Analysis

### 2023-06-17 TKT_RNAseq/R Code/EdgeR_Analysis.Rmd
TKT Heatmap app

>>>>

TKT.EdgeR = data.frame(GRF.CxDf = GR.F.CxDf[row.names(cpmdata),'FDR'],
                       GRF.CxOE = GR.F.CxOE[row.names(cpmdata),'FDR'],

                       WTF.CxDf = WT.F.CxDf[row.names(cpmdata),'FDR'],
                       WTF.CxOE = WT.F.CxOE[row.names(cpmdata),'FDR'],

                       GRxWT.FC = GRxWT.F[row.names(cpmdata),'FDR'],
                       GRxWT.FDf = GRxWT.FDf[row.names(cpmdata),'FDR'],
                       GRxWT.FOE = GRxWT.FOE[row.names(cpmdata),'FDR'],

                       GRM.CxDf = GR.M.CxDf[row.names(cpmdata),'FDR'],
                       GRM.CxOE = GR.M.CxOE[row.names(cpmdata),'FDR'],

                       WTM.CxDf = WT.M.CxDf[row.names(cpmdata),'FDR'],
                       WTM.CxOE = WT.M.CxOE[row.names(cpmdata),'FDR'],

                       GRxWT.MC = GRxWT.M[row.names(cpmdata),'FDR'],
                       GRxWT.MDf = GRxWT.MDf[row.names(cpmdata),'FDR'],
                       GRxWT.MOE = GRxWT.MOE[row.names(cpmdata),'FDR'])

row.names(TKT.EdgeR) = row.names(cpmdata)
##write.csv(TKT.EdgeR, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT.EdgeR.Table.csv")
